Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-08 draft.tex
make proof of prop 1 match defn 2

The strategies for the government and secessionists in this equilibrium are to play their best responses in the stage game given the continuation values induced by the investments of the outside actors. Unless otherwise noted below, playing Status Quo is the best response for both inside actors. The strategies for the insides actors are the following, organized according to the patron's investments in each state variable. In period $t$:

@@

To understand this equilibrium, notice that there are three possible ways to disturb the Status Quo: (1) the international community can provoke the secessionists to Cede, (2) the patron can provoke the government to cede, or (3) the patron can provoke the secessionists to fight.\footnote{The international community might also provoke the government to fight, but it is assumed to avoid conflict.} In order for the Status Quo Equilibrium to persist, each of these three disturbances must be deterred.

@@

\vskip.1in
\noindent {\bf Proof of Proposition 1} \\
Recall that each period is composed of three action stages: player $p$'s investment decision (stage 1), player $c$'s investment decision (stage 2), and the simultaneous game between players $g$ and $s$ (stage 3). Although period $t$ may be reached either because in period $t-1$ both players ceded or the status quo had been maintained, the strategic landscape in period $t$ is the same. Thus all periods in which the players are able to move are in an equivalence class in which the only possible strategic difference is in the value of the state variables.

Analysis of the posited equilibrium proceeds most naturally by backward induction within each period. Thus we begin with the stage game between the government and secessionists. We assume that the government and secessionists choose the Status Quo strategy whenever indifferent between it and any other strategy.

@@

Lemma 1 establishes ranges for the payoffs for players $g$ and $s$---gross of investments by the outside players---in which the status quo outcome can occur. The rest of this section tackles the more difficult task of determining the incentives and actions of the outside actors---that is, the patron state and the international community---to impact those payoffs.

@@

By contributing $\mu$ in each period, the patron supplies sufficient resources to the unrecognized state to ensure that the secessionist elite prefers the status quo to surrendering independence.   \hfill $\blacksquare$

>>>>

The strategies for the government and secessionists in this equilibrium are to play their best responses in the stage game given the continuation values induced by the investments of the outside actors. Unless otherwise noted below, playing Status Quo is the best response for both inside actors. The strategies for the insides actors are the following, organized according to the patron's investments in each relevant state variable. In period $t$:

@@

To understand the construction of this equilibrium, notice that there are three possible ways to disturb the Status Quo: (1) the international community can provoke the secessionists to Cede, (2) the patron can provoke the government to cede, or (3) the patron can provoke the secessionists to fight.\footnote{The international community might also provoke the government to fight, but it is assumed to avoid conflict.} In order for the Status Quo Equilibrium to persist, each of these three disturbances must be deterred.

@@

\vskip.1in
\noindent {\bf Proof of Proposition 1} \\
Recall that each period is composed of three action stages: player $p$'s investment decision (stage 1), player $c$'s investment decision (stage 2), and the simultaneous game between players $g$ and $s$ (stage 3). Although period $t$ may be reached either because in period $t-1$ both players ceded or the status quo had been maintained, the strategic landscape in period $t$ is the same given our restriction to stationary Markov strategies.

To establish that the Status Quo Equilibrium of Definition 2 exists, we must show that the given strategies constitute a Nash equilibrium in each subgame within a period given the induced continuation values.\footnote{Subgame perfection within the one-shot game combined with the stationary Markovian property ensures subgame perfection in the whole game.} We begin with the stage game between the government and secessionists. We assume that the government and secessionists choose the Status Quo strategy whenever indifferent between it and any other strategy.

@@

Lemma 1 establishes ranges for the payoffs for players $g$ and $s$---gross of investments by the outside players---in which the status quo outcome can occur.

We now turn to the incentives of the outside actors---that is, the patron state and the international community---in the subgames that begin in the first and second stages.

@@

Lemmas 2 through 4 establish that the only incentive compatible investment is that of the patron to deter the international community from inducing reunification, supported by the strategies described in cases (1)-(3) in Definition 2. This combined with Lemma 1 ensures the existence of the Status Quo Equilibrium described in Definition 2. \hfill $\blacksquare$
